### 2024-12-23 project3/draft.tex
ee
new

We further investigate the performance of fine-tuning on the target task of metamodeling GMMB contract losses on RS-GBM with dynamic lapse. 
The source tasks used for pretraining are GMMB contracts on RS-GBM with no lapse and static lapse, respectively. 
Figure~\ref{fig3:figure2} displays the learning curves of the LSTM metamodels fine-tuned from these two distinct source tasks.
We observe that the performance of the fine-tuned metamodel is highly dependent on the similarity between the source and target tasks.
Fine-tuning from a source task with static lapse results in faster convergence and lower validation error.
The metamodel trained on the GMMB with static lapse captures some features that are beneficial for the GMMB with dynamic lapse, which leads to a more stable training process.
In Figure~\ref{subfig3-2:fromNolapse}, the metamodel needs to learn the effect of 
\begin{itemize}
    \item whether lapse is present and
    \item whether the lapse is dynamic.
\end{itemize}
This learning process is more challenging.

@@

Table~\ref{tab3:transfer_learning_results_gmwb} summarizes the true MSEs of the LSTM metamodels on the GMWB contracts.
The TL methods are compared to training from scratch.
The suboptimal performance of layer freezing in this context indicates that the difference between the source and target tasks is too substantial for this method to be effective. 
While layer freezing can be advantageous when the source and target tasks are closely related, it may hinder performance when the tasks diverge significantly.
In such circumstances, fine-tuning provides a better approach by allowing the metamodel to leverage transferable knowledge while adapting to the new task's specific requirements. 
Fine-tuning enables both the LSTM and fully connected layers to update their weights, capturing the complex dynamics of the GMWB contracts more effectively.
This is particularly beneficial when developing metamodels for complex VA contracts with limited simulation data. 
For instance, transferring information from GMMB contracts can still be valuable when modeling GMWB contracts.
Both contracts share some common contract features and temporal patterns, which allows a pre-trained LSTM metamodel to capture generalizable features that provide a solid foundation for the target task.

@@

Figure~\ref{fig3:figure4-1} illustrates the performance of the two-stage procedure with TL for GMWB contracts with dynamic lapse in predicting the tail scenarios and the $95\%$-CVaR.
The graph provides a visual representation of how different TL approaches compare to training from scratch and the standard nested simulation procedure.
Fine-tuning consistently outperforms both layer freezing and training from scratch across different simulation budgets, particularly in predicting tail scenarios and estimating the 95\%-CVaR. 
This finding is consistent with the training history and MSEs in Figure~\ref{fig3:figure4} and Table~\ref{tab3:transfer_learning_results_gmwb}, respectively.
It's important to note that while these results are promising, they also highlight the complexity of modeling GMWB contracts with dynamic lapse. 
The fact that fine-tuning outperforms layer freezing suggests that there are significant differences in the tail behavior of GMMB and GMWB contracts, particularly when dynamic lapse is considered. 
This underscores the need for careful model selection and validation when applying TL techniques to different VA products.
When the source and target tasks are substantially different, all layers need to be updated, thus freezing some layers may lead to negative transfer.

@@

>>>>

We further investigate the performance of fine-tuning on the target task of metamodeling GMMB contract losses on RS-GBM with dynamic lapse. 
The source tasks used for pretraining are GMMB contracts on RS-GBM with no lapse and static lapse, respectively. 
Figure~\ref{fig3:figure2} displays the learning curves of the LSTM metamodels fine-tuned from these two distinct source tasks.
We observe that the performance of the fine-tuned metamodel is highly dependent on the similarity between the source and target tasks.
Fine-tuning from a source task with static lapse results in faster convergence and lower validation error.
The metamodel trained on the GMMB with static lapse captures some features that are beneficial for the GMMB with dynamic lapse, which leads to a more stable training process.
In Figure~\ref{subfig3-2:fromNolapse}, the metamodel needs to learn the effect of 
\begin{itemize}
    \item whether lapse is present, and
    \item whether the lapse is dynamic.
\end{itemize}
This makes learning more challenging.

@@

Table~\ref{tab3:transfer_learning_results_gmwb} summarizes the true MSEs of the LSTM metamodels on the GMWB contracts.
Training MSE and true MSE are computed using the training labels and the true contract losses approximated with $\num{100000}$ inner replications, respectively.
This is consistent with the terminology used in Chapter~\ref{chap:project2}.
The TL methods are compared to training from scratch.
The suboptimal performance of layer freezing in this context indicates that the difference between the source and target tasks is too substantial for this method to be effective. 
While layer freezing can be advantageous when the source and target tasks are closely related, it may hinder performance when the tasks diverge significantly.
In such circumstances, fine-tuning provides a better approach by allowing the metamodel to leverage transferable knowledge while adapting to the new task's specific requirements. 
Fine-tuning enables both the LSTM and fully connected layers to update their weights, capturing the complex dynamics of the GMWB contracts more effectively.
This is particularly beneficial when developing metamodels for complex VA contracts with limited simulation data. 
For instance, transferring information from GMMB contracts can still be valuable when modeling GMWB contracts.
Both contracts share some common contract features and temporal patterns, which allows a pre-trained LSTM metamodel to capture generalizable features that provide a solid foundation for the target task.

@@

Figure~\ref{fig3:figure4-1} illustrates the performance of the two-stage procedure with TL for GMWB contracts with dynamic lapse in predicting the tail scenarios and the $95\%$-CVaR.
The graph provides a visual representation of how different TL approaches compare to training from scratch and the standard nested simulation procedure.
Fine-tuning consistently outperforms both layer freezing and training from scratch across different simulation budgets, particularly in predicting tail scenarios and estimating the 95\%-CVaR. 
This finding is consistent with the training history and MSEs in Figure~\ref{fig3:figure4} and Table~\ref{tab3:transfer_learning_results_gmwb}, respectively.
It's important to note that while these results are promising, they also highlight the complexity of modeling GMWB contracts with dynamic lapse. 
The fact that fine-tuning outperforms layer freezing suggests that there are significant differences in the tail behavior of GMMB and GMWB contracts, particularly when dynamic lapse is considered. 
These findings highlight the need for careful model selection and validation when applying TL techniques to different VA products.
When the source and target tasks are substantially different, all layers need to be updated.
Freezing some layers may lead to negative transfer.

@@

\subsection{}
